### 2024-03-07 SRC/Data_Prep/Data_prep.Rmd
updated structure by reformatting files

# Cleaning the Data
movie_data <- read_csv(movie_data)

So after retrieving and mergig our data directly form the IMBD site, we now need to chcek and clean the data. In this markdown the data set is cleaned, reformatted and restructured.

@@

@@

>>>>

# Cleaning the Data
So after retrieving and mergig our data directly form the IMBD site, we now need to chcek and clean the data. In this markdown the data set is cleaned, reformatted and restructured.

@@

```{r reformatting the data, message=FALSE, warning=FALSE}
movie_data <- read_csv(movie_data)

movie_data <- movie_data %>%
  mutate(across(c(tconst, directors, writers, titleType, isAdult,genres, parentTconst,region,language,isOriginalTitle), as.factor)) %>%
  mutate(across(c(averageRating,numVotes,runtimeMinutes, title,seasonNumber, episodeNumber), as.numeric)) %>%
  mutate(across(c(primaryTitle, originalTitle,types, attributes),as.string))
```

@@

```{r}
movie_data <- movie_data %>%
  filter(numVotes > 100) 
```

# IV data_set

Now that we have clean
